---
dataMaid: yes
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations      14082

Number of variables            37
---------------------------------




# Codebook summary table

-----------------------------------------------------------------------
Label   Variable           Class       # unique  Missing  Description  
                                         values                        
------- ------------------ --------- ---------- --------- -------------
        **[cohort]**       factor             2  0.00 %                

        **[belong]**       numeric          850  0.40 %                

        **[sex]**          factor             2  0.00 %                

        **[indig]**        factor             2  0.00 %                

        **[loc]**          factor             2  0.00 %                

        **[immig]**        factor             3  1.62 %                

        **[egp]**          factor             4  16.38 %               

        **[escs]**         numeric         6937  0.54 %                

        **[sch\_grad1]**   numeric            3  0.23 %                

        **[sch\_grad2]**   numeric            3  10.45 %               

        **[sch\_grad3]**   numeric            3  20.98 %               

        **[sch\_grad4]**   numeric            3  33.14 %               

        **[pc1]**          numeric        14082  0.00 %                

        **[pc2]**          numeric        14082  0.00 %                

        **[pc3]**          numeric        14082  0.00 %                

        **[pc4]**          numeric        14081  0.00 %                

        **[pc5]**          numeric        14082  0.00 %                

        **[pc6]**          numeric        14082  0.00 %                

        **[pc7]**          numeric        14082  0.00 %                

        **[pc8]**          numeric        14082  0.00 %                

        **[pc9]**          numeric        14081  0.00 %                

        **[pc10]**         numeric        14082  0.00 %                

        **[neet1]**        factor             3  2.54 %                

        **[neet2]**        factor             3  10.45 %               

        **[neet3]**        factor             3  20.98 %               

        **[neet4]**        factor             3  33.14 %               

        **[sch\_pc1]**     numeric         1044  0.00 %                

        **[sch\_pc2]**     numeric         1044  0.00 %                

        **[sch\_pc3]**     numeric         1044  0.00 %                

        **[sch\_pc4]**     numeric         1044  0.00 %                

        **[sch\_pc5]**     numeric         1044  0.00 %                

        **[sch\_escs]**    numeric         1044  0.01 %                

        **[sch\_pc6]**     numeric          731  66.60 %               

        **[sch\_pc7]**     numeric          731  66.60 %               

        **[sch\_pc8]**     numeric          731  66.60 %               

        **[sch\_pc9]**     numeric          731  66.60 %               

        **[sch\_pc10]**    numeric          731  66.60 %               
-----------------------------------------------------------------------




# Variable list
## cohort

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                      factor

Number of missing obs.            0 (0 %)

Number of unique values                 2

Mode                        "cohort_2003"

Reference category            cohort_2003
-----------------------------------------


\emini
\bminitwo
```{r 'Var-1-cohort', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("cohort_2003", 
"cohort_2015"), class = "factor"), y = c(9378L, 4704L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "cohort")
```

\emini


- Observed factor levels: \"cohort_2003\", \"cohort_2015\". 



\fullline

## belong

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.       57 (0.4 %)

Number of unique values             849

Median                            -0.29

1st and 3rd quartiles       -0.64; 0.49

Min. and max.               -3.38; 2.61
---------------------------------------


\emini
\bminitwo
```{r 'Var-2-belong', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3.5, -3, -2.5, -2, 
-1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5), xmax = c(-3, -2.5, -2, 
-1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(43L, 5L, 105L, 263L, 
1099L, 3739L, 2498L, 3276L, 1181L, 739L, 174L, 724L, 179L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "belong")
```

\emini




\fullline

## sex

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                1
-----------------------------------


\emini
\bminitwo
```{r 'Var-3-sex', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("1", 
"2"), class = "factor"), y = c(7249L, 6833L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "sex")
```

\emini


- Observed factor levels: \"1\", \"2\". 



\fullline

## indig

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-4-indig', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(12988L, 1094L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "indig")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## loc

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-5-loc', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(5698L, 8384L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "loc")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## immig

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                     factor

Number of missing obs.      228 (1.62 %)

Number of unique values                2

Mode                                 "0"

Reference category                     0
----------------------------------------


\emini
\bminitwo
```{r 'Var-6-immig', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(10916L, 2938L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "immig")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## egp

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      2306 (16.38 %)

Number of unique values                  3

Mode                            "salariat"

Reference category            intermediate
------------------------------------------


\emini
\bminitwo
```{r 'Var-7-egp', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, .Label = c("intermediate", 
"salariat", "working"), class = "factor"), y = c(1721L, 9638L, 
417L)), class = "data.frame", row.names = c(NA, -3L)), vnam = "egp")
```

\emini


- Observed factor levels: \"intermediate\", \"salariat\", \"working\". 



\fullline

## escs

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.      76 (0.54 %)

Number of unique values            6936

Median                             0.36

1st and 3rd quartiles       -0.24; 0.91

Min. and max.               -4.06; 3.18
---------------------------------------


\emini
\bminitwo
```{r 'Var-8-escs', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(1L, 0L, 8L, 13L, 61L, 156L, 583L, 1527L, 2479L, 3080L, 
3208L, 2068L, 716L, 101L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "escs")
```

\emini




\fullline

## sch\_grad1

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.      32 (0.23 %)

Number of unique values               2

Median                                0

1st and 3rd quartiles              0; 0

Min. and max.                      0; 1
---------------------------------------


\emini
\bminitwo
```{r 'Var-9-sch-grad1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(13444L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 606L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad1")
```

\emini




\fullline

## sch\_grad2

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.      1472 (10.45 %)

Number of unique values                  2

Median                                   0

1st and 3rd quartiles                 0; 1

Min. and max.                         0; 1
------------------------------------------


\emini
\bminitwo
```{r 'Var-10-sch-grad2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(9432L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 3178L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad2")
```

\emini




\fullline

## sch\_grad3

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.      2955 (20.98 %)

Number of unique values                  2

Median                                   1

1st and 3rd quartiles                 1; 1

Min. and max.                         0; 1
------------------------------------------


\emini
\bminitwo
```{r 'Var-11-sch-grad3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(1815L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 9312L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad3")
```

\emini




\fullline

## sch\_grad4

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.      4667 (33.14 %)

Number of unique values                  2

Median                                   1

1st and 3rd quartiles                 1; 1

Min. and max.                         0; 1
------------------------------------------


\emini
\bminitwo
```{r 'Var-12-sch-grad4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(785L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 8630L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad4")
```

\emini




\fullline

## pc1

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.07

1st and 3rd quartiles       -0.66; 0.71

Min. and max.               -4.17; 3.17
---------------------------------------


\emini
\bminitwo
```{r 'Var-13-pc1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(2L, 6L, 21L, 96L, 288L, 663L, 1241L, 1882L, 2495L, 
2797L, 2366L, 1460L, 567L, 157L, 38L, 3L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc1")
```

\emini




\fullline

## pc2

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.06

1st and 3rd quartiles       -0.67; 0.71

Min. and max.                -4.4; 3.27
---------------------------------------


\emini
\bminitwo
```{r 'Var-14-pc2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(4L, 4L, 16L, 102L, 304L, 640L, 1237L, 1895L, 2500L, 
2782L, 2372L, 1431L, 593L, 169L, 29L, 4L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc2")
```

\emini




\fullline

## pc3

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.05

1st and 3rd quartiles       -0.67; 0.71

Min. and max.               -4.03; 3.53
---------------------------------------


\emini
\bminitwo
```{r 'Var-15-pc3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 2L, 21L, 87L, 299L, 655L, 1245L, 1908L, 2518L, 
2773L, 2303L, 1475L, 583L, 173L, 34L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc3")
```

\emini




\fullline

## pc4

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14081

Median                             0.06

1st and 3rd quartiles        -0.67; 0.7

Min. and max.               -4.61; 3.45
---------------------------------------


\emini
\bminitwo
```{r 'Var-16-pc4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-5, -4.5, -4, -3.5, 
-3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4.5, 
-4, -3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 
3, 3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 2L, 6L, 21L, 89L, 279L, 676L, 1258L, 1841L, 
2566L, 2760L, 2357L, 1430L, 583L, 180L, 31L, 2L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc4")
```

\emini




\fullline

## pc5

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.05

1st and 3rd quartiles       -0.66; 0.71

Min. and max.               -4.26; 3.26
---------------------------------------


\emini
\bminitwo
```{r 'Var-17-pc5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(3L, 5L, 21L, 89L, 289L, 672L, 1221L, 1973L, 2490L, 
2733L, 2344L, 1421L, 638L, 150L, 28L, 5L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc5")
```

\emini




\fullline

## pc6

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.06

1st and 3rd quartiles       -0.67; 0.72

Min. and max.               -4.17; 3.06
---------------------------------------


\emini
\bminitwo
```{r 'Var-18-pc6', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(2L, 6L, 26L, 92L, 283L, 655L, 1248L, 1914L, 2484L, 
2764L, 2379L, 1455L, 587L, 147L, 38L, 2L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc6")
```

\emini




\fullline

## pc7

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.05

1st and 3rd quartiles       -0.68; 0.72

Min. and max.                -4.4; 3.39
---------------------------------------


\emini
\bminitwo
```{r 'Var-19-pc7', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(4L, 4L, 15L, 106L, 297L, 635L, 1207L, 1973L, 2507L, 
2739L, 2359L, 1431L, 605L, 162L, 33L, 5L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc7")
```

\emini




\fullline

## pc8

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.05

1st and 3rd quartiles       -0.66; 0.71

Min. and max.               -4.03; 3.53
---------------------------------------


\emini
\bminitwo
```{r 'Var-20-pc8', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 4L, 20L, 88L, 316L, 633L, 1239L, 1900L, 2568L, 
2727L, 2347L, 1447L, 582L, 167L, 38L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc8")
```

\emini




\fullline

## pc9

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14081

Median                             0.05

1st and 3rd quartiles        -0.66; 0.7

Min. and max.               -4.61; 3.45
---------------------------------------


\emini
\bminitwo
```{r 'Var-21-pc9', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-5, -4.5, -4, -3.5, 
-3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4.5, 
-4, -3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 
3, 3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 2L, 5L, 23L, 87L, 275L, 682L, 1250L, 1889L, 
2576L, 2690L, 2363L, 1434L, 593L, 183L, 28L, 1L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc9")
```

\emini




\fullline

## pc10

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.06

1st and 3rd quartiles       -0.67; 0.71

Min. and max.                -4.26; 3.2
---------------------------------------


\emini
\bminitwo
```{r 'Var-22-pc10', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(2L, 4L, 20L, 98L, 289L, 672L, 1230L, 1946L, 2457L, 
2766L, 2304L, 1493L, 621L, 151L, 25L, 4L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc10")
```

\emini




\fullline

## neet1

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                     factor

Number of missing obs.      357 (2.54 %)

Number of unique values                2

Mode                                 "0"

Reference category                     0
----------------------------------------


\emini
\bminitwo
```{r 'Var-23-neet1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(13270L, 455L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet1")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet2

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      1472 (10.45 %)

Number of unique values                  2

Mode                                   "0"

Reference category                       0
------------------------------------------


\emini
\bminitwo
```{r 'Var-24-neet2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(11915L, 695L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet2")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet3

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      2955 (20.98 %)

Number of unique values                  2

Mode                                   "0"

Reference category                       0
------------------------------------------


\emini
\bminitwo
```{r 'Var-25-neet3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(10371L, 756L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet3")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet4

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      4667 (33.14 %)

Number of unique values                  2

Mode                                   "0"

Reference category                       0
------------------------------------------


\emini
\bminitwo
```{r 'Var-26-neet4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(8919L, 496L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet4")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## sch\_pc1

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.02

1st and 3rd quartiles       -0.34; 0.33

Min. and max.               -2.74; 2.01
---------------------------------------


\emini
\bminitwo
```{r 'Var-27-sch-pc1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(2L, 10L, 64L, 249L, 1952L, 4991L, 4505L, 1923L, 
329L, 56L, 1L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "sch_pc1")
```

\emini




\fullline

## sch\_pc2

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                                0

1st and 3rd quartiles       -0.35; 0.35

Min. and max.               -2.32; 1.68
---------------------------------------


\emini
\bminitwo
```{r 'Var-28-sch-pc2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.4, -2.2, -2, -1.8, 
-1.6, -1.4, -1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 
0.8, 1, 1.2, 1.4, 1.6), xmax = c(-2.2, -2, -1.8, -1.6, -1.4, 
-1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 1, 1.2, 
1.4, 1.6, 1.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 6L, 8L, 50L, 31L, 45L, 
202L, 454L, 869L, 1527L, 1475L, 2442L, 2052L, 1942L, 1260L, 867L, 
427L, 234L, 72L, 102L, 16L)), class = "data.frame", row.names = c(NA, 
-21L)), vnam = "sch_pc2")
```

\emini




\fullline

## sch\_pc3

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.02

1st and 3rd quartiles       -0.34; 0.33

Min. and max.               -2.29; 2.21
---------------------------------------


\emini
\bminitwo
```{r 'Var-29-sch-pc3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.5, -2, -1.5, -1, 
-0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2, -1.5, -1, -0.5, 0, 0.5, 
1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(8L, 
64L, 277L, 1926L, 4873L, 4537L, 1935L, 404L, 56L, 2L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "sch_pc3")
```

\emini




\fullline

## sch\_pc4

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.02

1st and 3rd quartiles       -0.35; 0.34

Min. and max.               -2.73; 2.05
---------------------------------------


\emini
\bminitwo
```{r 'Var-30-sch-pc4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 9L, 58L, 262L, 2058L, 4832L, 4439L, 1938L, 
430L, 54L, 1L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "sch_pc4")
```

\emini




\fullline

## sch\_pc5

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.01

1st and 3rd quartiles       -0.36; 0.33

Min. and max.                  -2.27; 2
---------------------------------------


\emini
\bminitwo
```{r 'Var-31-sch-pc5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.5, -2, -1.5, -1, 
-0.5, 0, 0.5, 1, 1.5), xmax = c(-2, -1.5, -1, -0.5, 0, 0.5, 1, 
1.5, 2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(13L, 65L, 
234L, 2042L, 4792L, 4526L, 2014L, 339L, 57L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "sch_pc5")
```

\emini




\fullline

## sch\_escs

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.       1 (0.01 %)

Number of unique values            1044

Median                              0.3

1st and 3rd quartiles       -0.04; 0.61

Min. and max.               -2.83; 1.61
---------------------------------------


\emini
\bminitwo
```{r 'Var-32-sch-escs', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(4L, 
0L, 1L, 21L, 241L, 3571L, 5558L, 3728L, 954L, 3L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "sch_escs")
```

\emini




\fullline

## sch\_pc6

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.      9378 (66.6 %)

Number of unique values               730

Median                              -0.01

1st and 3rd quartiles          -0.34; 0.4

Min. and max.                 -2.45; 2.07
-----------------------------------------


\emini
\bminitwo
```{r 'Var-33-sch-pc6', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.5, -2, -1.5, -1, 
-0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2, -1.5, -1, -0.5, 0, 0.5, 
1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(8L, 
43L, 191L, 585L, 1540L, 1433L, 752L, 135L, 16L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "sch_pc6")
```

\emini




\fullline

## sch\_pc7

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.      9378 (66.6 %)

Number of unique values               730

Median                              -0.01

1st and 3rd quartiles         -0.35; 0.42

Min. and max.                 -2.46; 2.18
-----------------------------------------


\emini
\bminitwo
```{r 'Var-34-sch-pc7', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.5, -2, -1.5, -1, 
-0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2, -1.5, -1, -0.5, 0, 0.5, 
1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(12L, 
44L, 171L, 572L, 1588L, 1408L, 758L, 100L, 49L, 2L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "sch_pc7")
```

\emini




\fullline

## sch\_pc8

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.      9378 (66.6 %)

Number of unique values               730

Median                               0.02

1st and 3rd quartiles         -0.36; 0.38

Min. and max.                 -2.89; 2.47
-----------------------------------------


\emini
\bminitwo
```{r 'Var-35-sch-pc8', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 9L, 52L, 209L, 566L, 1441L, 1484L, 751L, 
176L, 13L, 2L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "sch_pc8")
```

\emini




\fullline

## sch\_pc9

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.      9378 (66.6 %)

Number of unique values               730

Median                                  0

1st and 3rd quartiles         -0.36; 0.39

Min. and max.                 -2.75; 2.24
-----------------------------------------


\emini
\bminitwo
```{r 'Var-36-sch-pc9', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 7L, 46L, 191L, 590L, 1498L, 1465L, 723L, 
160L, 21L, 2L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "sch_pc9")
```

\emini




\fullline

## sch\_pc10

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.      9378 (66.6 %)

Number of unique values               730

Median                               0.01

1st and 3rd quartiles          -0.37; 0.4

Min. and max.                 -2.28; 2.17
-----------------------------------------


\emini
\bminitwo
```{r 'Var-37-sch-pc10', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.5, -2, -1.5, -1, 
-0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2, -1.5, -1, -0.5, 0, 0.5, 
1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(6L, 
29L, 191L, 603L, 1482L, 1441L, 797L, 138L, 16L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "sch_pc10")
```

\emini




\fullline



Report generation information:

 *  Created by: Philip Parker (username: `philipparker`).

 *  Report creation time: Tue Aug 31 2021 10:08:37

 *  Report was run from directory: `/Users/philipparker/Dropbox/Projects_Research/IN REVIEW/belonging_NEET`

 *  dataMaid v1.4.0 [Pkg: 2019-12-10 from CRAN (R 4.0.0)]

 *  R version 4.0.3 (2020-10-10).

 *  Platform: x86_64-apple-darwin17.0 (64-bit)(macOS Big Sur 10.16).

 *  Function call: `dataMaid::makeDataReport(data = combined_data %>% select(-schid), 
    render = FALSE, mode = c("summarize", "visualize", "check"
    ), smartNum = FALSE, file = "/Users/philipparker/Dropbox/Projects_Research/IN REVIEW/belonging_NEET/documentation/codebook.pdf", 
    replace = TRUE, standAlone = FALSE, checks = list(character = "showAllFactorLevels", 
        factor = "showAllFactorLevels", labelled = "showAllFactorLevels", 
        haven_labelled = "showAllFactorLevels", numeric = NULL, 
        integer = NULL, logical = NULL, Date = NULL), listChecks = FALSE, 
    maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for combined_data %>% select(-schid)")`

