---
dataMaid: yes
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations      14082

Number of variables            27
---------------------------------




# Codebook summary table

-----------------------------------------------------------------------
Label   Variable           Class       # unique  Missing  Description  
                                         values                        
------- ------------------ --------- ---------- --------- -------------
        **[cohort]**       factor             2  0.00 %                

        **[belong]**       numeric          850  0.40 %                

        **[sex]**          factor             2  0.00 %                

        **[indig]**        factor             2  0.00 %                

        **[loc]**          factor             2  0.00 %                

        **[immig]**        factor             3  1.62 %                

        **[egp]**          factor             4  16.38 %               

        **[escs]**         numeric         6937  0.54 %                

        **[sch\_grad1]**   numeric            3  0.23 %                

        **[sch\_grad2]**   numeric            3  10.45 %               

        **[sch\_grad3]**   numeric            3  20.98 %               

        **[sch\_grad4]**   numeric            3  33.14 %               

        **[pc1]**          numeric        14082  0.00 %                

        **[pc2]**          numeric        14082  0.00 %                

        **[pc3]**          numeric        14082  0.00 %                

        **[pc4]**          numeric        14081  0.00 %                

        **[pc5]**          numeric        14082  0.00 %                

        **[neet1]**        factor             3  2.54 %                

        **[neet2]**        factor             3  10.45 %               

        **[neet3]**        factor             3  20.98 %               

        **[neet4]**        factor             3  33.14 %               

        **[sch\_pc1]**     numeric         1044  0.00 %                

        **[sch\_pc2]**     numeric         1044  0.00 %                

        **[sch\_pc3]**     numeric         1044  0.00 %                

        **[sch\_pc4]**     numeric         1044  0.00 %                

        **[sch\_pc5]**     numeric         1044  0.00 %                

        **[sch\_escs]**    numeric         1044  0.01 %                
-----------------------------------------------------------------------




# Variable list
## cohort

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                      factor

Number of missing obs.            0 (0 %)

Number of unique values                 2

Mode                        "cohort_2003"

Reference category            cohort_2003
-----------------------------------------


\emini
\bminitwo
```{r 'Var-1-cohort', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("cohort_2003", 
"cohort_2015"), class = "factor"), y = c(9378L, 4704L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "cohort")
```

\emini


- Observed factor levels: \"cohort_2003\", \"cohort_2015\". 



\fullline

## belong

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.       57 (0.4 %)

Number of unique values             849

Median                            -0.29

1st and 3rd quartiles       -0.64; 0.49

Min. and max.               -3.38; 2.61
---------------------------------------


\emini
\bminitwo
```{r 'Var-2-belong', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3.5, -3, -2.5, -2, 
-1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5), xmax = c(-3, -2.5, -2, 
-1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(43L, 5L, 105L, 263L, 
1099L, 3739L, 2498L, 3276L, 1181L, 739L, 174L, 724L, 179L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "belong")
```

\emini




\fullline

## sex

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                1
-----------------------------------


\emini
\bminitwo
```{r 'Var-3-sex', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("1", 
"2"), class = "factor"), y = c(7249L, 6833L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "sex")
```

\emini


- Observed factor levels: \"1\", \"2\". 



\fullline

## indig

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "0"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-4-indig', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(12988L, 1094L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "indig")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## loc

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "1"

Reference category                0
-----------------------------------


\emini
\bminitwo
```{r 'Var-5-loc', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(5698L, 8384L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "loc")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## immig

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                     factor

Number of missing obs.      228 (1.62 %)

Number of unique values                2

Mode                                 "0"

Reference category                     0
----------------------------------------


\emini
\bminitwo
```{r 'Var-6-immig', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(10916L, 2938L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "immig")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## egp

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      2306 (16.38 %)

Number of unique values                  3

Mode                            "salariat"

Reference category            intermediate
------------------------------------------


\emini
\bminitwo
```{r 'Var-7-egp', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, .Label = c("intermediate", 
"salariat", "working"), class = "factor"), y = c(1721L, 9638L, 
417L)), class = "data.frame", row.names = c(NA, -3L)), vnam = "egp")
```

\emini


- Observed factor levels: \"intermediate\", \"salariat\", \"working\". 



\fullline

## escs

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.      76 (0.54 %)

Number of unique values            6936

Median                             0.36

1st and 3rd quartiles       -0.24; 0.91

Min. and max.               -4.06; 3.18
---------------------------------------


\emini
\bminitwo
```{r 'Var-8-escs', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(1L, 0L, 8L, 13L, 61L, 156L, 583L, 1527L, 2479L, 3080L, 
3208L, 2068L, 716L, 101L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "escs")
```

\emini




\fullline

## sch\_grad1

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.      32 (0.23 %)

Number of unique values               2

Median                                0

1st and 3rd quartiles              0; 0

Min. and max.                      0; 1
---------------------------------------


\emini
\bminitwo
```{r 'Var-9-sch-grad1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(13444L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 606L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad1")
```

\emini




\fullline

## sch\_grad2

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.      1472 (10.45 %)

Number of unique values                  2

Median                                   0

1st and 3rd quartiles                 0; 1

Min. and max.                         0; 1
------------------------------------------


\emini
\bminitwo
```{r 'Var-10-sch-grad2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(9432L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 3178L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad2")
```

\emini




\fullline

## sch\_grad3

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.      2955 (20.98 %)

Number of unique values                  2

Median                                   1

1st and 3rd quartiles                 1; 1

Min. and max.                         0; 1
------------------------------------------


\emini
\bminitwo
```{r 'Var-11-sch-grad3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(1815L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 9312L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad3")
```

\emini




\fullline

## sch\_grad4

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.      4667 (33.14 %)

Number of unique values                  2

Median                                   1

1st and 3rd quartiles                 1; 1

Min. and max.                         0; 1
------------------------------------------


\emini
\bminitwo
```{r 'Var-12-sch-grad4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(785L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 8630L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad4")
```

\emini




\fullline

## pc1

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.07

1st and 3rd quartiles       -0.66; 0.71

Min. and max.               -4.17; 3.17
---------------------------------------


\emini
\bminitwo
```{r 'Var-13-pc1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(2L, 6L, 21L, 96L, 288L, 663L, 1241L, 1882L, 2495L, 
2797L, 2366L, 1460L, 567L, 157L, 38L, 3L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc1")
```

\emini




\fullline

## pc2

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.05

1st and 3rd quartiles       -0.67; 0.71

Min. and max.                -4.4; 3.27
---------------------------------------


\emini
\bminitwo
```{r 'Var-14-pc2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(5L, 4L, 16L, 96L, 308L, 635L, 1233L, 1939L, 2518L, 
2736L, 2383L, 1400L, 621L, 152L, 32L, 4L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc2")
```

\emini




\fullline

## pc3

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14082

Median                             0.05

1st and 3rd quartiles       -0.66; 0.71

Min. and max.               -4.03; 3.53
---------------------------------------


\emini
\bminitwo
```{r 'Var-15-pc3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 2L, 18L, 92L, 314L, 652L, 1244L, 1872L, 2534L, 
2783L, 2285L, 1498L, 587L, 163L, 33L, 3L, 1L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc3")
```

\emini




\fullline

## pc4

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           14081

Median                             0.05

1st and 3rd quartiles        -0.66; 0.7

Min. and max.               -4.61; 3.45
---------------------------------------


\emini
\bminitwo
```{r 'Var-16-pc4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-5, -4.5, -4, -3.5, 
-3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4.5, 
-4, -3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 
3, 3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 2L, 7L, 23L, 84L, 290L, 660L, 1251L, 1876L, 
2579L, 2704L, 2382L, 1427L, 582L, 179L, 33L, 2L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc4")
```

\emini




\fullline

## pc5

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values          14082

Median                            0.06

1st and 3rd quartiles       -0.66; 0.7

Min. and max.               -4.26; 3.2
--------------------------------------


\emini
\bminitwo
```{r 'Var-17-pc5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(2L, 5L, 21L, 95L, 285L, 677L, 1225L, 1929L, 2472L, 
2779L, 2333L, 1452L, 610L, 167L, 25L, 5L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc5")
```

\emini




\fullline

## neet1

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                     factor

Number of missing obs.      357 (2.54 %)

Number of unique values                2

Mode                                 "0"

Reference category                     0
----------------------------------------


\emini
\bminitwo
```{r 'Var-18-neet1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(13270L, 455L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet1")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet2

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      1472 (10.45 %)

Number of unique values                  2

Mode                                   "0"

Reference category                       0
------------------------------------------


\emini
\bminitwo
```{r 'Var-19-neet2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(11915L, 695L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet2")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet3

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      2955 (20.98 %)

Number of unique values                  2

Mode                                   "0"

Reference category                       0
------------------------------------------


\emini
\bminitwo
```{r 'Var-20-neet3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(10371L, 756L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet3")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet4

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      4667 (33.14 %)

Number of unique values                  2

Mode                                   "0"

Reference category                       0
------------------------------------------


\emini
\bminitwo
```{r 'Var-21-neet4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(8919L, 496L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet4")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## sch\_pc1

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.02

1st and 3rd quartiles       -0.34; 0.33

Min. and max.               -2.74; 2.01
---------------------------------------


\emini
\bminitwo
```{r 'Var-22-sch-pc1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(2L, 10L, 64L, 249L, 1952L, 4991L, 4505L, 1923L, 
329L, 56L, 1L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "sch_pc1")
```

\emini




\fullline

## sch\_pc2

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                                0

1st and 3rd quartiles       -0.35; 0.35

Min. and max.                  -2.27; 2
---------------------------------------


\emini
\bminitwo
```{r 'Var-23-sch-pc2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.5, -2, -1.5, -1, 
-0.5, 0, 0.5, 1, 1.5), xmax = c(-2, -1.5, -1, -0.5, 0, 0.5, 1, 
1.5, 2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(13L, 55L, 
271L, 2055L, 4719L, 4528L, 2037L, 347L, 57L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "sch_pc2")
```

\emini




\fullline

## sch\_pc3

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.02

1st and 3rd quartiles       -0.35; 0.34

Min. and max.               -2.28; 2.17
---------------------------------------


\emini
\bminitwo
```{r 'Var-24-sch-pc3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.5, -2, -1.5, -1, 
-0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2, -1.5, -1, -0.5, 0, 0.5, 
1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(6L, 
51L, 300L, 1908L, 4933L, 4496L, 1911L, 420L, 56L, 1L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "sch_pc3")
```

\emini




\fullline

## sch\_pc4

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.01

1st and 3rd quartiles       -0.35; 0.34

Min. and max.               -2.89; 2.47
---------------------------------------


\emini
\bminitwo
```{r 'Var-25-sch-pc4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 9L, 74L, 267L, 2036L, 4743L, 4560L, 1904L, 
433L, 53L, 2L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "sch_pc4")
```

\emini




\fullline

## sch\_pc5

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1044

Median                            -0.01

1st and 3rd quartiles       -0.35; 0.34

Min. and max.               -2.32; 1.68
---------------------------------------


\emini
\bminitwo
```{r 'Var-26-sch-pc5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.4, -2.2, -2, -1.8, 
-1.6, -1.4, -1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 
0.8, 1, 1.2, 1.4, 1.6), xmax = c(-2.2, -2, -1.8, -1.6, -1.4, 
-1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 1, 1.2, 
1.4, 1.6, 1.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 6L, 8L, 50L, 41L, 47L, 
163L, 416L, 887L, 1481L, 1589L, 2454L, 2181L, 1706L, 1243L, 1010L, 
383L, 259L, 39L, 62L, 56L)), class = "data.frame", row.names = c(NA, 
-21L)), vnam = "sch_pc5")
```

\emini




\fullline

## sch\_escs

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.       1 (0.01 %)

Number of unique values            1044

Median                              0.3

1st and 3rd quartiles       -0.04; 0.61

Min. and max.               -2.83; 1.61
---------------------------------------


\emini
\bminitwo
```{r 'Var-27-sch-escs', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(4L, 
0L, 1L, 21L, 241L, 3571L, 5558L, 3728L, 954L, 3L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "sch_escs")
```

\emini




\fullline



Report generation information:

 *  Created by: Philip Parker (username: `phparker`).

 *  Report creation time: Wed Jun 02 2021 11:40:28

 *  Report was run from directory: `/Users/phparker/Dropbox/Projects_Research/IN REVIEW/belonging_NEET`

 *  dataMaid v1.4.0 [Pkg: 2019-12-10 from CRAN (R 4.0.2)]

 *  R version 4.0.3 (2020-10-10).

 *  Platform: x86_64-apple-darwin17.0 (64-bit)(macOS Mojave 10.14.5).

 *  Function call: `dataMaid::makeDataReport(data = combined_data %>% select(-schid), 
    render = FALSE, mode = c("summarize", "visualize", "check"
    ), smartNum = FALSE, file = "/Users/phparker/Dropbox/Projects_Research/IN REVIEW/belonging_NEET/documentation/codebook.pdf", 
    replace = TRUE, standAlone = FALSE, checks = list(character = "showAllFactorLevels", 
        factor = "showAllFactorLevels", labelled = "showAllFactorLevels", 
        haven_labelled = "showAllFactorLevels", numeric = NULL, 
        integer = NULL, logical = NULL, Date = NULL), listChecks = FALSE, 
    maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for combined_data %>% select(-schid)")`

