---
dataMaid: yes
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations      49232

Number of variables            27
---------------------------------




# Codebook summary table

-----------------------------------------------------------------------
Label   Variable           Class       # unique  Missing  Description  
                                         values                        
------- ------------------ --------- ---------- --------- -------------
        **[cohort]**       factor             2  0.00 %                

        **[belong]**       numeric         1564  3.24 %                

        **[sex]**          factor             2  0.00 %                

        **[indig]**        factor             3  0.02 %                

        **[loc]**          factor             3  1.11 %                

        **[immig]**        factor             3  2.99 %                

        **[egp]**          factor             4  12.04 %               

        **[escs]**         numeric        16401  2.34 %                

        **[sch\_grad1]**   numeric            3  42.73 %               

        **[sch\_grad2]**   numeric            3  46.93 %               

        **[sch\_grad3]**   numeric            3  50.85 %               

        **[sch\_grad4]**   numeric            3  59.58 %               

        **[pc1]**          numeric        24901  1.11 %                

        **[pc2]**          numeric        24901  1.11 %                

        **[pc3]**          numeric        24901  1.11 %                

        **[pc4]**          numeric        24900  1.11 %                

        **[pc5]**          numeric        24901  1.11 %                

        **[neet1]**        factor             3  43.93 %               

        **[neet2]**        factor             3  46.93 %               

        **[neet3]**        factor             3  50.85 %               

        **[neet4]**        factor             3  59.58 %               

        **[sch\_pc1]**     numeric         1073  1.11 %                

        **[sch\_pc2]**     numeric         1073  1.11 %                

        **[sch\_pc3]**     numeric         1073  1.11 %                

        **[sch\_pc4]**     numeric         1073  1.11 %                

        **[sch\_pc5]**     numeric         1073  1.11 %                

        **[sch\_escs]**    numeric         1069  1.24 %                
-----------------------------------------------------------------------




# Variable list
## cohort

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                      factor

Number of missing obs.            0 (0 %)

Number of unique values                 2

Mode                        "cohort_2015"

Reference category            cohort_2003
-----------------------------------------


\emini
\bminitwo
```{r 'Var-1-cohort', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("cohort_2003", 
"cohort_2015"), class = "factor"), y = c(21963L, 27269L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "cohort")
```

\emini


- Observed factor levels: \"cohort_2003\", \"cohort_2015\". 



\fullline

## belong

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.      1593 (3.24 %)

Number of unique values              1563

Median                              -0.29

1st and 3rd quartiles         -0.64; 0.49

Min. and max.                 -3.38; 2.61
-----------------------------------------


\emini
\bminitwo
```{r 'Var-2-belong', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3.5, -3, -2.5, -2, 
-1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5), xmax = c(-3, -2.5, -2, 
-1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(245L, 17L, 345L, 941L, 
4079L, 12026L, 10440L, 9864L, 4301L, 1999L, 780L, 1681L, 921L
)), class = "data.frame", row.names = c(NA, -13L)), vnam = "belong")
```

\emini




\fullline

## sex

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                            "2"

Reference category                1
-----------------------------------


\emini
\bminitwo
```{r 'Var-3-sex', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("1", 
"2"), class = "factor"), y = c(24394L, 24838L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "sex")
```

\emini


- Observed factor levels: \"1\", \"2\". 



\fullline

## indig

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                    factor

Number of missing obs.      10 (0.02 %)

Number of unique values               2

Mode                                "0"

Reference category                    0
---------------------------------------


\emini
\bminitwo
```{r 'Var-4-indig', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(42522L, 6700L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "indig")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## loc

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                     factor

Number of missing obs.      548 (1.11 %)

Number of unique values                2

Mode                                 "1"

Reference category                     0
----------------------------------------


\emini
\bminitwo
```{r 'Var-5-loc', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(19755L, 28929L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "loc")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## immig

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                      factor

Number of missing obs.      1473 (2.99 %)

Number of unique values                 2

Mode                                  "0"

Reference category                      0
-----------------------------------------


\emini
\bminitwo
```{r 'Var-6-immig', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(38110L, 9649L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "immig")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## egp

\bminione

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                       factor

Number of missing obs.      5928 (12.04 %)

Number of unique values                  3

Mode                            "salariat"

Reference category            intermediate
------------------------------------------


\emini
\bminitwo
```{r 'Var-7-egp', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, .Label = c("intermediate", 
"salariat", "working"), class = "factor"), y = c(11097L, 30416L, 
1791L)), class = "data.frame", row.names = c(NA, -3L)), vnam = "egp")
```

\emini


- Observed factor levels: \"intermediate\", \"salariat\", \"working\". 



\fullline

## escs

\bminione

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.      1153 (2.34 %)

Number of unique values             16400

Median                              -0.06

1st and 3rd quartiles         -0.56; 0.51

Min. and max.                  -4.5; 3.18
-----------------------------------------


\emini
\bminitwo
```{r 'Var-8-escs', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(5L, 3L, 24L, 68L, 249L, 805L, 3141L, 8937L, 12332L, 
10431L, 7403L, 3615L, 935L, 120L, 7L, 4L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "escs")
```

\emini




\fullline

## sch\_grad1

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       numeric

Number of missing obs.      21037 (42.73 %)

Number of unique values                   2

Median                                    0

1st and 3rd quartiles                  0; 0

Min. and max.                          0; 1
-------------------------------------------


\emini
\bminitwo
```{r 'Var-9-sch-grad1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(26932L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 1263L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad1")
```

\emini




\fullline

## sch\_grad2

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       numeric

Number of missing obs.      23104 (46.93 %)

Number of unique values                   2

Median                                    0

1st and 3rd quartiles                  0; 1

Min. and max.                          0; 1
-------------------------------------------


\emini
\bminitwo
```{r 'Var-10-sch-grad2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(19375L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 6753L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad2")
```

\emini




\fullline

## sch\_grad3

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       numeric

Number of missing obs.      25036 (50.85 %)

Number of unique values                   2

Median                                    1

1st and 3rd quartiles                  1; 1

Min. and max.                          0; 1
-------------------------------------------


\emini
\bminitwo
```{r 'Var-11-sch-grad3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(4213L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 19983L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad3")
```

\emini




\fullline

## sch\_grad4

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       numeric

Number of missing obs.      29333 (59.58 %)

Number of unique values                   2

Median                                    1

1st and 3rd quartiles                  1; 1

Min. and max.                          0; 1
-------------------------------------------


\emini
\bminitwo
```{r 'Var-12-sch-grad4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.05, 0.1, 0.15, 
0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 
0.8, 0.85, 0.9, 0.95), xmax = c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 
0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 
0.9, 0.95, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(1873L, 0L, 0L, 0L, 0L, 0L, 0L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 18026L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "sch_grad4")
```

\emini




\fullline

## pc1

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values            24900

Median                              0.03

1st and 3rd quartiles         -0.7; 0.71

Min. and max.                -4.03; 3.49
----------------------------------------


\emini
\bminitwo
```{r 'Var-13-pc1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0
), ymax = c(4L, 8L, 50L, 215L, 865L, 2326L, 4747L, 6934L, 8639L, 
9092L, 7931L, 4854L, 2220L, 610L, 170L, 19L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc1")
```

\emini




\fullline

## pc2

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values            24900

Median                              0.02

1st and 3rd quartiles        -0.69; 0.71

Min. and max.                -4.27; 3.58
----------------------------------------


\emini
\bminitwo
```{r 'Var-14-pc2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(6L, 14L, 27L, 199L, 904L, 2288L, 4721L, 7028L, 
8704L, 9211L, 7672L, 4893L, 2156L, 670L, 167L, 23L, 1L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc2")
```

\emini




\fullline

## pc3

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values            24900

Median                              0.02

1st and 3rd quartiles        -0.69; 0.71

Min. and max.                 -3.9; 3.71
----------------------------------------


\emini
\bminitwo
```{r 'Var-15-pc3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4, -3.5, -3, -2.5, 
-2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5), xmax = c(-3.5, 
-3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(11L, 38L, 180L, 887L, 2474L, 4510L, 6995L, 8795L, 
    9124L, 7778L, 4810L, 2210L, 698L, 161L, 11L, 2L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "pc3")
```

\emini




\fullline

## pc4

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values            24899

Median                              0.03

1st and 3rd quartiles         -0.7; 0.71

Min. and max.                -4.48; 3.64
----------------------------------------


\emini
\bminitwo
```{r 'Var-16-pc4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(4L, 13L, 37L, 197L, 912L, 2272L, 4747L, 7074L, 
8589L, 9079L, 7767L, 4976L, 2166L, 663L, 163L, 23L, 2L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc4")
```

\emini




\fullline

## pc5

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values            24900

Median                              0.02

1st and 3rd quartiles        -0.69; 0.71

Min. and max.                -4.12; 3.56
----------------------------------------


\emini
\bminitwo
```{r 'Var-17-pc5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5), xmax = c(-4, 
-3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5, 2, 2.5, 3, 
3.5, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(3L, 6L, 46L, 207L, 833L, 2438L, 4633L, 7023L, 
8718L, 9054L, 7653L, 4979L, 2265L, 677L, 128L, 20L, 1L)), class = "data.frame", row.names = c(NA, 
-17L)), vnam = "pc5")
```

\emini




\fullline

## neet1

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                        factor

Number of missing obs.      21626 (43.93 %)

Number of unique values                   2

Mode                                    "0"

Reference category                        0
-------------------------------------------


\emini
\bminitwo
```{r 'Var-18-neet1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(26597L, 1009L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet1")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet2

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                        factor

Number of missing obs.      23104 (46.93 %)

Number of unique values                   2

Mode                                    "0"

Reference category                        0
-------------------------------------------


\emini
\bminitwo
```{r 'Var-19-neet2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(24559L, 1569L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet2")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet3

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                        factor

Number of missing obs.      25036 (50.85 %)

Number of unique values                   2

Mode                                    "0"

Reference category                        0
-------------------------------------------


\emini
\bminitwo
```{r 'Var-20-neet3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(22392L, 1804L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet3")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## neet4

\bminione

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                        factor

Number of missing obs.      29333 (59.58 %)

Number of unique values                   2

Mode                                    "0"

Reference category                        0
-------------------------------------------


\emini
\bminitwo
```{r 'Var-21-neet4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("0", 
"1"), class = "factor"), y = c(18707L, 1192L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "neet4")
```

\emini


- Observed factor levels: \"0\", \"1\". 



\fullline

## sch\_pc1

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values             1073

Median                             -0.03

1st and 3rd quartiles         -0.36; 0.3

Min. and max.                -2.36; 2.08
----------------------------------------


\emini
\bminitwo
```{r 'Var-22-sch-pc1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.4, -2.2, -2, -1.8, 
-1.6, -1.4, -1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 
0.8, 1, 1.2, 1.4, 1.6, 1.8, 2), xmax = c(-2.2, -2, -1.8, -1.6, 
-1.4, -1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8, 2, 2.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
0L, 14L, 62L, 30L, 118L, 243L, 1623L, 3167L, 5571L, 6568L, 8021L, 
7778L, 5473L, 4225L, 3139L, 1270L, 706L, 226L, 140L, 232L, 35L, 
42L)), class = "data.frame", row.names = c(NA, -23L)), vnam = "sch_pc1")
```

\emini




\fullline

## sch\_pc2

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values             1073

Median                             -0.02

1st and 3rd quartiles        -0.37; 0.31

Min. and max.                 -1.8; 2.25
----------------------------------------


\emini
\bminitwo
```{r 'Var-23-sch-pc2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1.8, -1.6, -1.4, -1.2, 
-1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 1, 1.2, 1.4, 
1.6, 1.8, 2, 2.2), xmax = c(-1.6, -1.4, -1.2, -1, -0.8, -0.6, 
-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 1, 1.2, 1.4, 1.6, 1.8, 2, 
2.2, 2.4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(18L, 59L, 29L, 279L, 1957L, 2901L, 
5707L, 6164L, 8044L, 7726L, 6036L, 3997L, 3080L, 1277L, 775L, 
213L, 83L, 171L, 126L, 0L, 42L)), class = "data.frame", row.names = c(NA, 
-21L)), vnam = "sch_pc2")
```

\emini




\fullline

## sch\_pc3

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values             1073

Median                             -0.03

1st and 3rd quartiles        -0.35; 0.32

Min. and max.                -2.82; 2.04
----------------------------------------


\emini
\bminitwo
```{r 'Var-24-sch-pc3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), xmax = c(-2.5, -2, -1.5, -1, -0.5, 
0, 0.5, 1, 1.5, 2, 2.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 9L, 70L, 492L, 6962L, 17488L, 16153L, 6075L, 
1036L, 356L, 42L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "sch_pc3")
```

\emini




\fullline

## sch\_pc4

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values             1073

Median                             -0.03

1st and 3rd quartiles         -0.37; 0.3

Min. and max.                 -2.2; 2.15
----------------------------------------


\emini
\bminitwo
```{r 'Var-25-sch-pc4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-2.2, -2, -1.8, -1.6, 
-1.4, -1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8, 2), xmax = c(-2, -1.8, -1.6, -1.4, -1.2, 
-1, -0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 1, 1.2, 1.4, 
1.6, 1.8, 2, 2.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(12L, 5L, 20L, 58L, 
149L, 236L, 1366L, 3417L, 5961L, 6158L, 7867L, 7501L, 5885L, 
4474L, 2707L, 1252L, 851L, 348L, 163L, 65L, 147L, 42L)), class = "data.frame", row.names = c(NA, 
-22L)), vnam = "sch_pc4")
```

\emini




\fullline

## sch\_pc5

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      548 (1.11 %)

Number of unique values             1073

Median                             -0.01

1st and 3rd quartiles         -0.37; 0.3

Min. and max.                 -3.1; 1.98
----------------------------------------


\emini
\bminitwo
```{r 'Var-26-sch-pc5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-3.5, -3, -2.5, -2, 
-1.5, -1, -0.5, 0, 0.5, 1, 1.5), xmax = c(-3, -2.5, -2, -1.5, 
-1, -0.5, 0, 0.5, 1, 1.5, 2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0), ymax = c(1L, 0L, 9L, 67L, 504L, 7485L, 16717L, 16475L, 
5949L, 1063L, 414L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "sch_pc5")
```

\emini




\fullline

## sch\_escs

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.      611 (1.24 %)

Number of unique values             1069

Median                             -0.08

1st and 3rd quartiles        -0.32; 0.22

Min. and max.                -4.06; 1.32
----------------------------------------


\emini
\bminitwo
```{r 'Var-27-sch-escs', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-4.5, -4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1), xmax = c(-4, -3.5, -3, 
-2.5, -2, -1.5, -1, -0.5, 0, 0.5, 1, 1.5), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 0L, 0L, 3L, 0L, 0L, 
54L, 4418L, 22996L, 16114L, 4402L, 633L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "sch_escs")
```

\emini




\fullline



Report generation information:

 *  Created by: Philip Parker (username: `philipparker`).

 *  Report creation time: Thu Feb 04 2021 11:52:32

 *  Report was run from directory: `/Users/philipparker/Dropbox/Projects_Research/CURRENT_WORKING/belonging_NEET`

 *  dataMaid v1.4.0 [Pkg: 2019-12-10 from CRAN (R 4.0.2)]

 *  R version 4.0.2 (2020-06-22).

 *  Platform: x86_64-apple-darwin17.0 (64-bit)(macOS  10.16).

 *  Function call: `dataMaid::makeDataReport(data = combined_data %>% select(-schid), 
    render = FALSE, mode = c("summarize", "visualize", "check"
    ), smartNum = FALSE, file = "/Users/philipparker/Dropbox/Projects_Research/CURRENT_WORKING/belonging_NEET/documentation/codebook.pdf", 
    replace = TRUE, standAlone = FALSE, checks = list(character = "showAllFactorLevels", 
        factor = "showAllFactorLevels", labelled = "showAllFactorLevels", 
        haven_labelled = "showAllFactorLevels", numeric = NULL, 
        integer = NULL, logical = NULL, Date = NULL), listChecks = FALSE, 
    maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for combined_data %>% select(-schid)")`

